Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity

### 2022-02-15 paper.tex
Fixing R7: taking onset as t=27 as seem in KE fig 2b

\begin{figure*}
  \centering
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy-4.pdf}
      \caption{Kinetic Energy}
      \label{fig:kink_ke-4}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy_log-4.pdf}
      \caption{Growth rate estimation}
      \label{fig:kink_ke_log-4}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{heating_r-4.pdf}
      \caption{Internal energy, with viscous and Ohmic heating}
      \label{fig:heating-4}
    \end{subfigure}
  \mycaption{Kinetic energy and heating as a function of time showing the development and
  measured growth rates $\gamma$ and $\lambda$ of the flute and kink
  instabilities, respectively.}{Resistivity is $\eta=10^{-4}$ and Figure~\ref{fig:kink_ke_log-4} is a enlarged version of the first. \rev{The viscous heating associated with the flute instability (that generated before $t\approx28$) is negligible compared to that associated with the kink instability. While the isotropic model permits greater viscous heating (on the order of two orders of magnitude), the anisotropic model enhances Ohmic heating.}}
\label{fig:kink_str8_ke-4}%
\end{figure*}

@@

We now describe the evolution and competition of flute and kink instabilities
in case of resistivity $\eta=10^{-4}$. Figure~\ref{fig:kink_pressure_slices-4}
shows the \rev{gas} pressure profile of the anisotropic viscosity case
\eqref{eq:switching_model} at time moments $t=26$, $28$ and $30$ and at $z=0$.
At $t=26$ the tube becomes unstable \rev{to the flute instability} with azimuthal
wavenumber $m=4$, when the plasma begins to  bulge out diagonally from the
high-pressure core as seen in Figure~\ref{fig:swi-4_pressure_13}. As  the
bulges move radially outwards into lower \rev{gas} pressure regions they expand and
accelerate, resulting in the entire \rev{gas} pressure structure \rev{\newold{}{appearing}} taking the
shape of a four-leaf clover (Figure~\ref{fig:swi-4_pressure_14}). By $t=30$ the
kink instability has disrupted the flute instability and is developing
nonlinearly as evident in Figure~\ref{fig:swi-4_pressure_15}. As is typical of
nonlinear kink development, the tube continues to release its stored potential
energy in the form of kinetic energy and heat and the contained plasma becomes
highly mixed. In the  isotropic viscosity case which will not be illustrated by
a separate figure, the flute instability is present but \rev{its
 growth is damped relative to the anisotropic case}, and it is 
outcompeted by the kink instability which quickly dominates the dynamics.

@@

Table~\ref{tab:kink_fluting_params} summarises the quantitative differences
between the results for the two values of the resistivity $\eta$ and two models
of viscosity. \rev{The mean across the radius of the ideal estimate of the
growth rate~\eqref{eq:fluting_growth_rate2} provides the theoretical average
growth rate, which is in decent agreement with the observed rate in each case,
particularly in the more ideal case where $\eta=10^{-4}$. The location of the
peak growth rate provides a prediction of where the instability will initially
grow. This radius is used in conjunction with the resonance
equation~\eqref{eq:resonant_surface} (with $m=4$) to predict the axial
wavenumber of the perturbation with the greatest linear growth, i.e. the
perturbation most likely to be observed. Again, these are in good agreement
with the observed fluting wavenumbers, which are measured at times just prior
to the nonlinear development of the flute instability, that is at $t=22$ when
$\eta=10^{-3}$ and $t=26$ when $\eta = 10^{-4}$. The kink wavenumber is
measured at $t=26$ in both cases. Overall, the agreement between predicted and observed growth rates and perturbation wavenumbers allows us to conclude that the observed instability is the ideal flute instability and that the growth rate~\eqref{eq:fluting_growth_rate2} can be effectively applied to the instability within coronal loops.}

>>>>

\begin{figure*}
  \centering
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy-4.pdf}
      \caption{Kinetic Energy}
      \label{fig:kink_ke-4}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy_log-4.pdf}
      \caption{Growth rate estimation}
      \label{fig:kink_ke_log-4}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{heating_r-4.pdf}
      \caption{Viscous and Ohmic heating}
      \label{fig:heating-4}
    \end{subfigure}
  \mycaption{Kinetic energy \rev{and heating} as a function of time showing the development and
  measured growth rates $\gamma$ and $\lambda$ of the flute and kink
  instabilities, respectively.}{Resistivity is $\eta=10^{-4}$ and Figure~\ref{fig:kink_ke_log-4} is a enlarged version of the first. \rev{The viscous heating associated with the flute instability (that generated before $t\approx28$) is negligible compared to that associated with the kink instability. While the isotropic model permits greater viscous heating (on the order of two orders of magnitude), the anisotropic model enhances Ohmic heating.}}
\label{fig:kink_str8_ke-4}%
\end{figure*}

@@

We now describe the evolution and competition of flute and kink instabilities
in case of resistivity $\eta=10^{-4}$. Figure~\ref{fig:kink_pressure_slices-4}
shows the \rev{gas} pressure profile of the anisotropic viscosity case
\eqref{eq:switching_model} at time moments $t=26$, $28$ and $30$ and at $z=0$.
\rev{At approximately $t\approx 27$} the tube becomes unstable \rev{to
the flute instability} \rev{as observed from the linear growth phase
  of the kinetic energy shown in Figure
  \ref{fig:kink_str8_ke-4}(b)}. The the plasma begins to  bulge out
diagonally from the high-pressure core displaying an azimuthal
wavenumber $m=4$ as seen in Figure~\ref{fig:swi-4_pressure_13}. As  the
bulges move radially outwards into lower \rev{gas} pressure regions they expand and
accelerate, resulting in the entire \rev{gas} pressure structure \rev{\newold{}{appearing}} taking the
shape of a four-leaf clover (Figure~\ref{fig:swi-4_pressure_14}). By $t=30$ the
kink instability has disrupted the flute instability and is developing
nonlinearly as evident in Figure~\ref{fig:swi-4_pressure_15}. As is typical of
nonlinear kink development, the tube continues to release its stored potential
energy in the form of kinetic energy and heat and the contained plasma becomes
highly mixed. In the  isotropic viscosity case which will not be illustrated by
a separate figure, the flute instability is present but \rev{its
 growth is damped relative to the anisotropic case}, and it is 
outcompeted by the kink instability which quickly dominates the dynamics.

@@

Table~\ref{tab:kink_fluting_params} summarises the quantitative differences
between the results for the two values of the resistivity $\eta$ and two models
of viscosity. \rev{The mean across the radius of the ideal estimate of the
growth rate~\eqref{eq:fluting_growth_rate2} provides the theoretical average
growth rate, which is in decent agreement with the observed rate in each case,
particularly in the more ideal case where $\eta=10^{-4}$. The location of the
peak growth rate provides a prediction of where the instability will initially
grow. This radius is used in conjunction with the resonance
equation~\eqref{eq:resonant_surface} (with $m=4$) to predict the axial
wavenumber of the perturbation with the greatest linear growth, i.e. the
perturbation most likely to be observed. Again, these are in good agreement
with the observed fluting wavenumbers, which are measured at times just prior
to the accelerated development of the flute instability, that is at $t=22$ when
$\eta=10^{-3}$ and $t=26$ when $\eta = 10^{-4}$. The kink wavenumber is
measured at $t=26$ in both cases. Overall, the agreement between predicted and observed growth rates and perturbation wavenumbers allows us to conclude that the observed instability is the ideal flute instability and that the growth rate~\eqref{eq:fluting_growth_rate2} can be effectively applied to the instability within coronal loops.}
